### 2019-08-28 README.Rmd
upd README

Spatiotemporal extensions for mlr3

[![Travis build status](https://travis-ci.org/mlr-org/mlr3spatiotemporal.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3spatiotemporal)
[![CRAN status](https://www.r-pkg.org/badges/version/mlr3spatiotemporal)](https://cran.r-project.org/package=mlr3spatiotemporal)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotemporal/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotemporal?branch=master)

@@

- Spatial CV using k-means clustering after Brenning2012 (ResampleCVKmeans) (package [sperrorest](https://github.com/pat-s/sperrorest)))

The following ones are planned:

- "Spatial Blocking" (package [blockCV](https://github.com/rvalavi/blockCV))
- "Environmental Blocking" (package [blockCV](https://github.com/rvalavi/blockCV))
- "Buffering" (package [blockCV](https://github.com/rvalavi/blockCV))

@@

@@

———. 2012. “Spatial Cross-Validation and Bootstrap for the Assessment of
Prediction Rules in Remote Sensing: The R Package Sperrorest.” In *2012
IEEE International Geoscience and Remote Sensing Symposium*, 5372–5.
<https://doi.org/10.1109/IGARSS.2012.6352393>.

>>>>

Spatio-temporal extensions for mlr3

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mlr-org/mlr3spatiotemporal.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3spatiotemporal)
[![CRAN status](https://www.r-pkg.org/badges/version/mlr3spatiotemporal)](https://cran.r-project.org/package=mlr3spatiotemporal)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotemporal/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotemporal?branch=master)
<!-- badges: end -->

@@

| Literature Name | R Package | Reference | mlr3spatiotemporal Name |
| --------------- | --------- | --------- | ----------------------- |
| Spatial CV  | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResampleSpCVCoords`  |
| Spatial Blocking | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVBlock`   |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVEnv`   |
| Spatial Buffering | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVBuffer` |

@@

Generic S3 function `autoplot()` for all implemented spatial resampling methods.

@@

**Brenning**, A.. 2012. “Spatial Cross-Validation and Bootstrap for the Assessment of
Prediction Rules in Remote Sensing: The R Package Sperrorest.” In *2012
IEEE International Geoscience and Remote Sensing Symposium*, 5372–5.
<https://doi.org/10.1109/IGARSS.2012.6352393>.

<div id="ref-Valavi2019">

**Valavi** R, Elith J, Lahoz-Monfort JJ, Guillera-Arroita G. blockCV: An r package for generating spatially or environmentally separated folds for k-fold cross-validation of species distribution models. Methods Ecol Evol. 2019; 10:225–232. doi.org/10.1111/2041-210X.13107
